\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Harjot Singh}

\address{\faGithub{ github.com/harjotsb6} \faLink{ linkedin.com/in/harjotsb6} \faEnvelope{ harjotsb56@gmail.com}}

\begin{document}

\begin{rSection}{Education}

{\bf Bhavans Vivekanada College } \hfill {\em Expected Grad. 2022} 
\\{ \textit {Bachelors in Computer Application \\& Course work: Discrete maths, OOP's(C/C++/Java), DBMS, AI ...  }} 

{\bf Delhi Public School} \hfill {\em  2019} 
\\ { \textit {Metric and Intermediate \\& Course work: Commerce, Economics, Civics, Accountancy ...}} \hfill

\end{rSection}

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: \ & C, C++, Java, Python, HTML/CSS, Javascipt, SQL/MYSQL  \\
Frameworks \& Tools: & Numpy, Pandas, ScikitLearn, Git/Github\\
\end{tabular}

\end{rSection}

\begin{rSection}{Projects}

{\bf Dog Vision}
\\- Built a deep learning project on identifying breed of dogs using a Convolutional Neural Network(CNN) built using Tensor Flow.
\\- Built a model using Transfer Learning, help of MobileNetV2  convolution blocks.
\\-  Applied custom user images to identify the model with almost 90\% accuracy. 

{\bf Cardiovascular Disease Dataset}
\\- Constructed a machine learning model from scratch using Supervised Learning and Logistic Regression as the estimator.
\\- Goal was to achieve a Cross-Validated score of 80\% or more and the model surpassed the minimum score by 85-90\%, with highest Recall score close to 90\% of the model.
\\-Hyper-tuned the model and its parameters to achieve 1-2\% boost on existing model.

{\bf Pima Diabetic Dataset}
\\- Aggregated and prepped 800 patients records of National Institute of Diabetes and Digestive and Kidney Diseases from independent source of data set.
\\- Created a logistic regression and KNN model in SAS, combining disparate sources into one projection that outperformed with 82\%  accuracy.

\end{rSection}

\begin{rSection}{Work Experience}

{\bf MVARO ( www.mvaro.com )} \hfill {\em July 2021\\} 
{\textit{Machine Learning Internship}}
\\- Goal was to create a digit recognizer using MNIST dataset. To see the effectiveness of methods on reduced data sets and one- shot learning, smaller modified versions of MNIST were created. 
\\- To reduce time complexity and further improve performance, different variant of SVM (Support Vector Machine) was used.

\end{rSection}

\end{document}
